Model Search in Relational Domains

### 2016-10-21 learning.tex
decision level

However, rule (3) is domain-specific and only applies to numerical abstract
domains \pscmt{???}.  For example, let $C = \langle x+z \geq 10,  w \geq 0 \rangle$ 
be a conflicting element that does not satisfy $\varphi$ and let $a= \langle x+y \geq 2, y+z \geq 5,

@@

\paragraph {\textbf{Backjumping}}
A backjumping procedure undoes all the assignments in the trail up to 
a decision level \pscmt{explained?} that restores the solver to a consistent state 
(non-conflicting).  The backjumping level is defined by the literal 
of the conflict clause that is closest to the root (decision level 0) 
where the conflict clause is still unit. If a conflict clause is 
globally unit, then the backjumping level is the root of the search tree.

>>>>

However, rule (3) is domain-specific and only applies to interval and octagon
domain.  For example, let $C = \langle x+z \geq 10,  w \geq 0 \rangle$ be a 
conflicting element that does not satisfy $\varphi$ and let $a= \langle x+y \geq 2, y+z \geq 5,

@@

\paragraph {\textbf{Backjumping}}
A backjumping procedure undoes all the assignments in the trail up to 
a decision level that restores the solver to a non-conflicting state.  
The backjumping level is defined by the literal of the conflict clause 
that is closest to the root (decision level 0) where the conflict 
clause is still unit.  If a conflict clause is globally unit, then the 
backjumping level is the root of the search tree.
